\section{Future Work}
For future investigation, we would focus on firstly evaluating the effect of training on corrupted
data which would hopefully improve model robustness. Second, we would evaluate combinations
of corruption types to better reflect real world scenarios. Finally we would hope to investigate
integrating our corruption framework along with the processed data, by first applying the
corruption on the raw data and performing the transformations necessary to produce the processed
data.

\section{Conclusion}
In this report, we introduced a structured sensor corruption framework for evaluating the
robustness of Human Activity Recognition models under realistic sensor degradation. Our framework
characterizes corruption along three dimensions: type, granularity, and severity, and applies
five fault types across accelerometer and gyroscope modalities of the UCI HAR dataset. We evaluated
four models trained on clean data and tested under controlled corruption, providing the first
baseline for additional corruption types than dropout.
Our experiments reveal that corruption types have different impacts on the models. Dropout, being
the most studied corruption type in prior literature, did not produce the most significant
degradation. However, bias and drift caused significant performance drops on most models. The
performance drop is due to these fault types altering the signal distribution that learned models
rely on.
These results highlight the need to focus on additional corruption types beyond dropout, which
additionally cannot be solved by imputation techniques. We hope our framework and baseline results
motivate future work on building HAR systems robust to more sensor fault types.
